### 2021-02-08 exploratory/2021/plots.Rmd
Fix header

```{r load_opticlust}
opticlust <- read_tsv(here('subworkflows/1_prep_samples/results/opticlust_results.tsv')) %>% 
  full_join(read_tsv(here('subworkflows/1_prep_samples/results/dataset_sizes.tsv'))) %>% 
  mutate_perf()
sum_opticlust <- opticlust %>% 
  group_by(dataset) %>% 
  summarize(mcc_median = median(mcc),
            sec_median = median(sec),
            mem_gb_median = median(mem_gb))#,
            #median_shannon = median(shannon))
```
```{r mcc_opticlust}
opticlust %>% 
  ggplot(aes(dataset, mcc)) +
  geom_jitter(alpha = 0.5) +
  ylim(0.5, 1)
```
```{r runtime_opticlust}
opticlust %>% 
  ggplot(aes(num_seqs, sec, color = dataset)) +
  geom_point(alpha = 0.5)
```
## fit to reference databases

```{r load_fit-dbs}
ref_sizes <- read_tsv(here('subworkflows/2_fit_reference_db/results/ref_sizes.tsv'))
optifit_dbs <- read_tsv(here('subworkflows/2_fit_reference_db/results/optifit_dbs_results.tsv')) %>% 
  mutate_perf()
head(optifit_dbs)
```

>>>>

```{r load_opticlust}
opticlust <- read_tsv(here('subworkflows/1_prep_samples/results/opticlust_results.tsv')) %>% 
  full_join(read_tsv(here('subworkflows/1_prep_samples/results/dataset_sizes.tsv'))) %>% 
  mutate_perf()
sum_opticlust <- opticlust %>% 
  group_by(dataset) %>% 
  summarize(mcc_median = median(mcc),
            sec_median = median(sec),
            mem_gb_median = median(mem_gb))#,
            #median_shannon = median(shannon))
```
```{r mcc_opticlust}
opticlust %>% 
  ggplot(aes(dataset, mcc)) +
  geom_jitter(alpha = 0.5) +
  ylim(0.5, 1)
```
```{r runtime_opticlust}
opticlust %>% 
  ggplot(aes(num_seqs, sec, color = dataset)) +
  geom_point(alpha = 0.5)
```

## fit to reference databases

```{r load_fit-dbs}
ref_sizes <- read_tsv(here('subworkflows/2_fit_reference_db/results/ref_sizes.tsv'))
optifit_dbs <- read_tsv(here('subworkflows/2_fit_reference_db/results/optifit_dbs_results.tsv')) %>% 
  mutate_perf()
```
